First Order Logic of Sparse Random Hyper-Graphs

### 2019-07-07 Presentacion/Presentación.tex
cambio tonto
Pictures

	\begin{frame}{The theorem}
		For each $1\leq i \leq c$ let $p_i(n,\beta_i)=\beta_i/n^{a_i-1}$. Let $\beta=(\beta_1,\dots,\beta_c)$ and 
		$p(n,\beta)=(p_1(n,\beta_i),\dots,p_c(n,\beta_c)$.

		\end{frame}
\end{document}

>>>>

	\begin{frame}{The theorem}
		We want to prove the following

		\begin{theorem} Let $\varphi$ be a first order sentence in $\mathcal{L}$.
			Then the map $\mathrm{F}:[0,\infty)^c\rightarrow \R$ given by
			\[ \mathrm{F}(\beta_1,\dots, \beta_c)= \Ln 
			\mathrm{Pr}(HG(n,p(n,\beta))\models \varphi )
			\]
			is well defined and admits an analytic extension to $\CC^c$. 
		\end{theorem}

	\begin{frame}{Distance and paths}
		Given any graph $G$, we define the following distance over its vertex-set:

			\begin{equation*}d(x,y)= \min_{\substack{H \leq G\\ 
					H \text{ connected }\\
					x,y\in V(H)}} \big(|V(H)| - 1 \big), \, \, \text{ or } \infty \text{ if }
				x,y \text{ are not connected.}
			\end{equation*}

		\begin{definition} 
			A path between two vertices $x,y$ in a graph $G$ is
			a connected subgraph $H\leq G$ containing both $x,y$ whose
			number of vertices is minimum. 
		\end{definition}

	\end{frame}
	\begin{frame}{Likelihood, trees, cycles and clusters} 
		\begin{definition}
			The likelihood $L(G)$ of a graph $G=(V,H_1,\dots,H_c)$ is
			the number
			\[ |V(G)| - \sum_{i=1}^c |H_i|(a_i-1).\]
		\end{definition}
	~\\
	\end{frame}

	\begin{frame}{Likelihood, trees, cycles and clusters} 
	\begin{itemize}
		\item A tree is a connected graph with likelihood $1$.
		\vspace*{0.5 em}
	\end{itemize}

	\begin{center}
		\includegraphics[width=0.7\linewidth]{Tree.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{Likelihood, trees, cycles and clusters} 
		\begin{itemize}
			\item An unicycle is a connected graph with likelihood $0$.
			A cycle is a minimal unicycle.
		\end{itemize}
		\begin{center}
			\includegraphics[width=0.9\linewidth]{Cycles.pdf}
		\end{center}
	\end{frame}

	\begin{frame}{Likelihood, trees, cycles and clusters}
		\begin{itemize}
			\item A cluster is a graph $G$ with $L(G)\leq 0$ such 
			that $L(H)>L(G)$\\ for any subgraph $H\leq G$.
		\end{itemize}
	\begin{center}
		\includegraphics[width=0.4\linewidth]{Cluster.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		A rooted $(T,x)$ is a tree $T$ together with a distinguished vertex
		$x\in V(T)$.\par
		\[Tree(y, T) = (T[X], y),\]
		\[\text{where } \, X=\{ z\in V(T) \, | \, d(x,z)=d(x,y)+d(y,z)\}.\]~\\
		The root of an edge $e\in H(T)$ in a rooted tree 
		$(T,x)$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.\\~\\
		The radius of an edge $e\in H(T)$ is 
		\[\max_{\substack{y\in e \\ y \text{ not the root of } e}} r(Tree(y,T)). \]

	\begin{frame}{The $k$-morphism relation over trees.}
		Fix $k\in \N$.\\
		We define the $k$-morphism relation over rooted trees of the same radius
		inductively as follows:

		\begin{itemize}
			\item If $r(T_1)=r(T_2)=0$ then $T_1\morph{k} T_2$.
		\end{itemize}
	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		For $r>0$:
			\begin{itemize}
				\item  First we
				define the type of a en edge with radius less than $r$:

			\end{itemize}
		\begin{center}
			\includegraphics[width=0.8\linewidth]{Edgetype.pdf}
		\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation over trees.}
		\begin{itemize}
		\item If $r(T_1)=r(T_2)=r$ we say that $T_1\morph{K}T_2$ if
		for any edge $k$-type $E$ of radius less than $r$ either:
		\begin{itemize}
			\vspace{0.2 em}
			\item the number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
			is the same, or
			\vspace{0.2 em}
			\item both $T_1$ and $T_2$ contain no less than $k+1$
			initial edges of $k$-type $E$. 
		\end{itemize}
		\begin{center}
			\includegraphics[width=0.7\linewidth]{Try.pdf}
		\end{center}

		\end{itemize}

\end{document}
